%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Hitesh}{Joshi}{ \urlstyle{same}\url{https://www.linkedin.com/in/hitesh-joshi-a9928613/} \\
\href{mailto:sendmailtojoshi@gmail.com}{sendmailtojoshi@gmail.com} \linebreak Ph - +91-9550660020
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UPTU, Lucknow}
\descript{B.Tech in Computer Science}
\location{Graduated 2008 | DIT University, Dehradun \\ Grade: 70\%}
\sectionsep


\subsection{Soar Valley Public School}
\location{Grad. May 2003 \\  Pithoragarh,Uttarakhand,India\\
Highschool: 83\%, Intermediate : 70\%  }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/hiteshjoshi1}{\custombold{@hiteshjoshi1}} \\
LinkedIn://  \href{https://www.linkedin.com/in/hitesh-joshi-a9928613/}{\custombold{@hitesh-joshi\-a9928613}} \\
Twitter://  \href{https://twitter.com/joshi_ji}{\custombold{@joshi\_ji}} \\
Blog:// \href{https://medium.com/@achiever.hitesh}{\custombold{@achiever.hitesh}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{} J2EE \textbullet{} Spring \textbullet{} Spring Boot \textbullet{} REST 
\textbullet{} NodeJs \textbullet{} Angular4  \textbullet{} JavaScript \textbullet{} Solidity \\
 
\location{Over 1000 lines:}
SocketIO \textbullet{} Python \textbullet{} \LaTeX\ \\
CSS \\
\sectionsep
\subsection{Operating Systems}
Linux \textbullet{} Unix   \textbullet{} Windows
\sectionsep
\subsection{Cloud}
Azure \textbullet{} Heroku \textbullet{} AWS(basic familiarity) 
\sectionsep
\subsection{Tools:}
\textbullet{} web3js \textbullet{} Truffle \textbullet{} Metamask \textbullet{} Ganache \textbullet{} Parity
\textbullet{} Quorum \textbullet{} Hyperledger Fabric \textbullet{} RabbitMq,\textbullet{}ActiveMQ, \textbullet{} Spring AMQP, \textbullet{} 
Netflix OSS, PEGA CSA.
\sectionsep
\subsection{Databases:}
Oracle\textbullet{} MongoDb \textbullet{} Mysql \textbullet{}Cassandra 
\sectionsep
\subsection{Architecture and problem solving}
Design patterns \textbullet{} Microservices \textbullet{} Data Structure \textbullet{} Algorithms \\

\section{Github repertoire}
\subsection{Blockchain}
\href{https://github.com/hiteshjoshi1/dns-dapp}{\custombold{@dapp}} \\
\subsection{Microservices}
\href{https://github.com/hiteshjoshi1/microservice-docker-cart-example}{\custombold{@microservices}} \\


\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{DELOITTE CONSULTING}
\descript{| Senior Consultant }
\location{Joined August 2013 | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working as a  Technical architect in Java-Microservices space and as a full stack developer in the Blockchain space.
\item Certified Scrum Master, currently leading a team of 30 practitioners as an engagement manager.
\item Hands on developer, more than 65 percent hands on daily.
\item Creating smart contracts in Solidity and DApps from scratch.
\item Creating Java or Nodejs based backend applications and Angular 4 based front end.
\item Hands on experience of building Microservices including service discovery, load balancing,circuit breaking,distributed log tracing, performance tuning, security,deployment and scaling.
\item Working on new RFP and RFI for Deloitte's clients.
\end{tightemize}
\sectionsep

\runsubsection{UHG}
\descript{| Software Engineer }
\location{Sept 2011 – Oct 2013 | Hyderabad, India}
\begin{tightemize}
\item Worked primarily on Java, J2EE, Spring, Hibernate, REST and SOAP based webservices.
\item Worked on front end HTML, CSS, JavaScript, deployment using Jenkins.
\end{tightemize}
\sectionsep

\runsubsection{General Electric (GE)}
\descript{| Software Developer}
\location{Sept 2009 – Aug 2011 | Hyderabad, India}
\begin{tightemize}
\item Java developer working on eMatrix.
\item Developed new internal GE applications and supported multiple production applications.
\item Worked with and managed multiple vendor technical practitioners.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{RECENT PROJECTS}
\runsubsection{Gordon Food - Vendor Agreements}
\descript{| Technical manager, Scrum Master}
\begin{tightemize}
\item Estimated and formalized project delivery timeliness,release scope, sprint scope, product backlog grooming and velocity estimation. 
\item Creating initial project structure, db design, code review checklist, sonar rules,git merge strategy, build and deployment via Jenkins,etc.
\end{tightemize}
\sectionsep

\runsubsection{Letter of Credit on Blockchain -  Kotak Mahindra Bank   }
\descript{| Chief Architect and lead developer}
\begin{tightemize}
\item Lead the development of solution from ground up, created the network, designed the smart contract.
\item Wrote the NodeJS api to interact with Blockchain as well as IPFS.
\item Deployed the application to Azure.
\end{tightemize}
\sectionsep

\runsubsection {Global Hp support website }\href{https://support.hp.com/us-en}{HP} 
\descript{| Technical Team Lead and Scrum master}
\begin{tightemize}
\item Lead developer on multi lingual, multi cluster hp.com/support built on JSR286 portlets, IBM websphere.
\item Worked on content ingestion in Mongodb, xslt parser, WCM integration, \end{tightemize}
\sectionsep
\end{minipage} 
\end{document}  \documentclass[]{article}